How to find epistasis, Bitches!

### 2013-08-21 docs/protocols_ms/epistasis_protocols.tex
added methods sections to first draft of a protocols manuscript

QC - probably want to use a hight MAF cut-off than a standard GWAS in order to as anything with low MAF is going to increase the probability of $p_1^2 * p_2^2 * n$ being less than a required level. \\
Normalisation (distribution with respect to models used). Normal data. Is it worth discussing the potential problems caused by a skew in $y$ and its effect on the tail of the test statistic distribution?  \\

@@

Reiterate the distinction between CPU and GPU. I guess we can re-calculate some of the speed differences based on current GPU hardware and show speed difference with relation to cpu based software. (God place for a figure)

@@

@@

>>>>

QC - probably want to use a high MAF cut-off than a standard GWAS in order to as anything with low MAF is going to increase the probability of $p_1^2 * p_2^2 * n$ being less than a required level. \\
Normalisation (distribution with respect to models used). Normal data. Is it worth discussing the potential problems caused by a skew in $y$ and its effect on the tail of the test statistic distribution?  \\

@@

Reiterate the distinction between CPU and GPU. I guess we can re-calculate some of the speed differences based on current GPU hardware and show speed difference with relation to cpu based software. (Good place for a figure)

@@

How to deal with multiple testing [what is the current state of your manuscript?]. Using GPUs it's not unrealistic that a researcher with access to a GPU cluster could run a permutation analysis for a single phenotype 2D scan. However, that should compare to your theoretically derived threshold. Therefore, the problem lies when we have multiple, correlated phenotypes such as expression.

@@

Remove SNP pairs that are in LD greater than (threshold). Could lead in appearance of effects. Threshold determined based on....?

Population stratification and cryptic relatedness - look for inflation of LD between snp pairs.

\section{Discussion}
